```{r}
movies <- read.csv("Movies.csv")
library(rmarkdown)
```
# Base R

## Univariate Visualiations of a Quantitative Variable

### Create a dot plot of runtime

```{r}
plot(
  x = movies$Runtime,
  y = rep(0, nrow(movies)),
  main = "Distribution of Movie Runtimes",
  xlab = "Runtime (minutes)",
  ylab = "",
  yaxt = "n"
)
```

### Create a dot plot with alpha transparency

```{r}
plot(
  x = movies$Runtime,
  y = rep(0, nrow(movies)),
  main = "Distribution of Movie Runtimes",
  xlab = "Runtime (minutes)",
  ylab = "",
  yaxt = "n",
  pch = 16,
  col = rgb(0, 0, 0, 0.1)
)
```

### Add jitter to dot plot

```{r}
plot(
  x = movies$Runtime,
  y = jitter(rep(0, nrow(movies))),
  main = "Distribution of Movie Runtimes",
  xlab = "Runtime (minutes)",
  ylab = "",
  yaxt = "n"
)
```

### Create a boxplot of runtime

```{r}
boxplot(
  x = movies$Runtime,
  horizontal = TRUE,
  main = "Distribution of Movie Runtimes",
  xlab = "Runtime (minutes)"
)
```

### Create a histogram of runtime

```{r}
hist(
  x = movies$Runtime,
  main = "Distribution of Movie Runtimes",
  xlab = "Runtime (minutes)"
)
```

### Create a course-grain histogram

```{r}
hist(
  x = movies$Runtime,
  main = "Distribution of Movie Runtimes",
  xlab = "Runtime (minutes)",
  breaks = 10
)
```

### Create a fine-grain histogram

```{r}
hist(
  x = movies$Runtime,
  main = "Distribution of Movie Runtimes",
  xlab = "Runtime (minutes)",
  breaks = 30
)
```

### Create a density plot of runtime

```{r}
plot(
  x = density(movies$Runtime),
  main = "Distribution of Movie Runtimes",
  xlab = "Runtime (minutes)"
)
```

### Create small multiples of all four

```{r}
par(mfrow = c(4,1))
```

```{r}
plot(
    x = movies$Runtime, 
    y = jitter(rep(0, nrow(movies))), 
    xlim = c(0, 250),
    main = "Distribution of Movie Runtimes",
    xlab = "",
    ylab = "", 
    yaxt = "n",
    pch = 16,
    col = rgb(0, 0, 0, 0.1))

boxplot(
    x = movies$Runtime,
    ylim = c(0, 250),
    horizontal = TRUE)

hist(
    x = movies$Runtime,
    xlim = c(0, 250),
    main = "",
    xlab = "",
    ylab = "",
    yaxt = "n")

plot(
    x = density(movies$Runtime),
    xlim = c(0, 250),
    main = "",
    xlab = "Runtime (minutes)",
    ylab = "",
    yaxt = "n")
```

### Reset multi-row display

```{r}
par(mfrow = c(1, 1))
```